### 2017-01-19 robust-software.tex
Minor tidying up and reformatting the checklist

>>>>

If you are new to version control,
it is simplest to treat it as ``a better \withurl{Dropbox}{http://dropbox.com}''
(or, if you are of a certain age, a better FTP),
and to use it simply to synchronize files between multiple developers and machines.
Once you are comfortable working that way,
you should \ruleminor{use a feature branch workflow}:
designate one parallel copy (or ``branch'') of the repository as the master,
and create a new branch from it each time you want to fix a bug or add a new feature.
This allows work on independent changes to proceed in isolation;
once the work has been completed and tested,
it can be merged into the master branch for release.

We also recommend that you \ruleminor{tag your releases}.
A ``tag'' is a label that marks a particular revision in a repository's history.
Adding such labels makes it much easier to find desired revisions at a later date,
and also makes it clear exactly what was released.
